---
title: "Crash data"
output: html_notebook
---

I asked NZTA for data on the number of crashes each hour since 2000. Crashes are
classified as Fatal, Serious injury, minor injury, and no injury.

Initially I am interested in understanding what the variations in the various ratios
of crash types over time - and during holiday periods.

```{r, include=F}
library(tidyverse)
library(ggthemes)
library(RPostgreSQL)
library(zoo)
library(lubridate)
db <- dbConnect(PostgreSQL(), dbname='crashes-18')
```

```{r, fig.height=20}
crashes <- tbl(db, "crashes") %>%
  collect() %>%
  mutate(month = as.yearmon(day)) %>%
  group_by(month) %>%
  summarise(fatal_all = sum(count[severity=="Fatal"])/sum(count)*100,
            fatal_all_injury = sum (count[severity %in% c("Fatal")]/sum(count[severity != "Non-injury"])*100),
            fatal_serious_all = sum (count[severity %in% c("Fatal", "Serious")]/sum(count)*100),
            fatal_serious_injury = sum (count[severity %in% c("Fatal", "Serious")]/
                                          sum(count[severity != "Non-injury"])*100)) %>%
  mutate(year=year(month))
```

Is there any monthly signal in the percentage of crashes which are fatal?

```{r, fig.height=20}
ggplot(crashes, aes(x=as.Date(month),y=fatal_all)) +
  geom_col() +
  facet_wrap(. ~ year, ncol=2, scales="free")
```

Is there any signal in the percentage of crashes which result in a fatality or a serious injury?

```{r, fig.height=20}
ggplot(crashes, aes(x=as.Date(month),y=fatal_serious_all)) +
  geom_col() +
  facet_wrap(. ~ year, ncol=2, scales="free")
```

What about if we remove non-injury crashes?

```{r, fig.height=20}
ggplot(crashes, aes(x=as.Date(month),y=fatal_serious_injury)) +
  geom_col() +
  facet_wrap(. ~ year, ncol=2, scales="free")
```